Ladies' figure skating in the 2002 Winter Olympics

### 2022-10-25 inst/skating.Rmd
slight improvement on skating_maxp

```{r,maxshow, cache = TRUE}
skating <- ordertable2supp(skating_table)
skating_maxp <- maxp(skating)
m <- skating_maxp # for ease of  typing
m
```

```{r equalskatingptest}
equalp.test(skating)
```

@@

@@

```{r plotapieofo}
(o <- maxp(o))
pie(o)
```

>>>>

```{r,maxshow, cache = TRUE}
skating <- ordertable2supp(skating_table)
options("use_alabama" = TRUE)
skating_maxp <- maxp(skating,startp=
c(5.0493913251e-06, 0.0053037393083, 0.090240695999, 
0.00036893464900, 1.1397045995e-05, 8.3424027249e-05, 
9.8129903007e-06, 0.00026960143514, 0.29831585124, 
0.001376333090, 2.9434081237e-06, 0.26550514587, 
0.00051946513092, 1.7e-06, 0.00080745068338, 
0.00029358481485, 0.00048852120227, 0.0053075302458, 
0.0025877438737, 0.30889220253, 1.2869403350e-05, 
0.0184563624305147))    # values from previous repeated runs of maxp()
m <- skating_maxp # for ease of  typing
m
```

```{r equalpskatingtest,cache=TRUE}
equalp.test(skating)
```

@@

We may test the hypothesis that Slutskaya == Kwan == Hughes:

```{r,testtop3,cache=TRUE}
samep.test(skating,c("slutskaya","kwan","hughes"))
```

@@

```{r plotapieofo,cache=TRUE}
(o <- maxp(o))
pie(o)
```
